Optimized and Cost Considering Huffman Code For Biological Data Transmission

### 2015-01-19 Article/Article.tex
issues biological data

%% main text
\section{Introduction}
\section{Background}
\subsection{Issues on Biological Data Transmission}
\subsection{Huffman Code}
\subsection{Power Efficient on Data Transmission}
\subsection{Unequal Bit Considering On data Transmission}
\section{Approach}
\subsection{Proposed Scheme}
\subsection{Power Efficient Huffman code}
\subsection{Optimisation of the Codes}
\section{Results And Discussion}
\section{Conclusion}

>>>>

%% main text
\section{Introduction}
\section{Background}
\subsection{Issues on Biological Data Transmission}
The size of biological data including DNA sequences increase with an ever expanding rate and will be bigger and bigger in the future. These Biological data are stored in biology database, the exponential growth of these database become a big problem to all biological data processing methods. 
Different operation will be applied to these data such as, searching [],e-mail attachment [], alignment [], and transmission on distributed computing []. Interestingly, biological data compression can play a key role in all biological data processing.

\subsection{Huffman Code}
\subsection{Power Efficient on Data Transmission}
\subsection{Unequal Bit Considering On data Transmission}
\section{Approach}
\subsection{Proposed Scheme}
\subsection{Power Efficient Huffman code}
\subsection{Optimisation of the Codes}
\section{Results And Discussion}
\section{Conclusion}
